Robust receding horizon control for linear systems with state and input dependent disturbances

### 2015-06-29 example.tex
Removed highlighting.

\section{Example}\label{sec:example}
In this section we present a numerical simulation for a simplified levitating ball model, as derived in~\cite{Schaich:2015}. \edit{The dynamics of the nonlinear system are given $m\ddot y = m g - c i^2/y^2$,
where $m$ denotes the mass of the ball, $g$ is the acceleration due to gravity, $c$ is a constant depending
on the coil, $y$ the vertical distance to the coil (Fig.~\ref{fig:levitating:ball}). We assume that the current~$i$ is directly specified by the controller, thus neglecting the inductive dynamics of the coil. %Figure~\ref{fig:levitating:ball} illustrates the setup.
Choosing the state $x=(y,\dot y)$ and the input $u=i$ we obtain a state space representation which depends nonlinearly
on the state and control input.} For any $x_1>0$, the system is in equilibrium if $x_2=0$ and $u=\sqrt{\frac{gm}{c}}x_1$.

>>>>

\section{Example}\label{sec:example}
In this section we present a numerical simulation for a simplified levitating ball model, as derived in~\cite{Schaich:2015}. The dynamics of the nonlinear system are given $m\ddot y = m g - c i^2/y^2$,
where $m$ denotes the mass of the ball, $g$ is the acceleration due to gravity, $c$ is a constant depending
on the coil, $y$ the vertical distance to the coil (Fig.~\ref{fig:levitating:ball}). We assume that the current~$i$ is directly specified by the controller, thus neglecting the inductive dynamics of the coil. %Figure~\ref{fig:levitating:ball} illustrates the setup.
Choosing the state $x=(y,\dot y)$ and the input $u=i$ we obtain a state space representation which depends nonlinearly
on the state and control input. For any $x_1>0$, the system is in equilibrium if $x_2=0$ and $u=\sqrt{\frac{gm}{c}}x_1$.

### 2015-06-29 post_review.tex
Removed highlighting.

\edit{In almost all existing methods for RMPC, the model disturbances are assumed to be confined to sets that are constant, i.e.~independent of the system state and control inputs. Disturbances that depend on model states (or control inputs) are considered in~\cite{Kuntsevich:1995,Rakovic:2006}. However general formulations of state and input dependence can result in non-convex constraints~\citep{Rakovic:2006}. To avoid this we make use of recent algorithmic advances~\citep{Schaich:2015} that enable a class of polytopic disturbance sets that depend affinely on the system state and control input to be handled using convex constraints. This provides an algorithmic and analytical framework which is used in the
current paper to embed affine state and input dependent disturbance constraints into the framework of the
active set RMPC solver framework proposed by~\cite{Buerger:2011}. Disturbances that belong to sets which depend
on model states and inputs can account for multiplicative model uncertainty as well as linearisation
errors, and the approach of this paper is therefore able to handle linearisation errors in RMPC non-conservatively.}

@@

\section{Problem Statement}\label{sec:problem:statement}
We consider a computationally efficient method for solving online min-max receding horizon control problems
that exploits the structure of multi-parametric programming solutions. Our approach determines the optimal
feedback law without approximating the cost or the constraints of the problem, and without making restrictive
assumptions on the parametrisation of control inputs.
%This broadens the applicability of the approach, allowing for higher order models and longer
%prediction horizons than 
%
%The high computational complexity of online min-max receding horizon control schemes generally requires either
%that the solution is approximated or that their application is limited to problems involving simple system models and short horizons. Here we consider an
%efficient method for solving min-max problems that exploits the structure of multi-parametric programming
%solutions.
%The set of systems to which a min-max robust receding horizon control scheme can be applied online 
%without approximating the solution is bounded by the system complexity. The way to solve min-max problems we 
%adopt here, is to use the structure of the solution to derive multi-parametric programs that can be solved
%efficiently. In order to be able to obtain a closed form solution of the min-max program simple optimisation
%formulations have to be
%The algorithmic treatment of min-max problems
%involving state constraints and disturbances constrained to lie in fixed polytopic disturbance sets was
%introduced in~\cite{Bertsekas:1971}. Recently~\cite{Schaich:2015} proposed an algorithm to compute the so called maximal
%robust positive invariant (MRPI) sets (see~\cite{blanchini:2007}) for linear systems subject to state and
%input dependent disturbance constraints. In this paper we develop the algorithm further
%to compute polytopic constraints necessary to satisfy state constraints robustly in this setup. We
%present a robust receding horizon control scheme for
%
To make it possible to obtain a closed form solution of the min-max optimal control problem we assume a
linear-quadratic problem formulation. Thus we assume linear dynamics 
\begin{equation}\label{eq:system:equation}
	x^+ = A x + B u + D w,
\end{equation}
%
where $A,B,D$ are real matrices of appropriate dimension, $x,  x^+\in\mathcal X\subseteq\mathbb R^n$ denote the state 
and successor state respectively, $u\in\mathcal U=\{u:F_iu\leq 1\,\forall i\in\mathcal I^{\mathcal U}\}
\subset\mathbb R^p$ is the control input
and $w\in\mathcal W(x,u)\subset\mathbb R^q$ is an unknown disturbance input, $\mathcal I^{\mathcal U}$ denotes
the index set of the constraint set~$\mathcal U$. The disturbance set $\mathcal
W(x,u)$ is assumed to have a known dependence on the values of $x$ and $u$, according to
%
\begin{equation}\label{eq:PWA:def:disturbance}
	\mathcal W(x,u) = \{w: Gw \leq H(x,u)\},
\end{equation}
%
\edit{where each element of $H(x,u)$ is a convex, piecewise affine function for all $(x,u)\in\mathcal X\times\mathcal U$}. 
%\edit{where $H(x,u)$ is an elementwise convex, piecewise affine function}.
The control objective is to minimize the
worst case value, over all future model uncertainty, of the cost
\begin{equation}\label{eq:quadratic:cost}
\sum_{k=0}^\infty \bigl( \norm{x_k}_Q^2 + \norm{u_k}_R^2 - \gamma^2 \norm{w_k}^2 \bigr) ,
\end{equation}
where the subscript $k$ denotes the realisation of a variable at time $k$, $\norm{x}_Q^2$ denotes the quadratic
form $x^TQx$, $Q$ and $R$ are given positive definite
matrices and $\gamma$ is a given scalar weight that controls the $l^2$-gain of the closed loop system from the
disturbance sequence to the state and control sequences.

@@

\section{Controllable sets}\label{sec:preliminaries}
In this section we summarise results on controllable sets that allow the constraints of the problem~\eqref{eq:the:problem} 
to be formulated in a convenient way. The following result shows that the MRPI set (\ref{eq:definition:MRPI:set}) 
associated with the pointwise polytopic set~\eqref{eq:PWA:def:disturbance} is polytopic if $H$ is elementwise convex 
and piecewise affine. For a proof and detailed discussion of this result we refer the reader to~\cite{Schaich:2015}.
%
\edit{\begin{thm}[\cite{Schaich:2015}]\label{thm:MRPI:set:is:polytopic}
Let $\mathcal X \subseteq \{x:\Gamma x\leq{\bf{1}}\wedge-\Gamma x\leq{\bf{1}}\}$ be a polyhedral set, let the pair $(A+BK,\Gamma)$ be
observable, and let $\mathcal W(x,Kx)$ be defined as in~\eqref{eq:PWA:def:disturbance} with an elementwise convex piecewise
affine function $H(x,Kx)$ which is bounded for all finite $x$. Then the MRPI set $\mathcal X^\infty$ is polytopic, i.e.\ it has the representation 
\begin{equation}\label{eq:halfspace:representation:MRPI}
	\mathcal X^\infty=\{x:\Lambda_i x\leq \lambda_i, \forall\, i\in\mathcal I^\infty\}.
\end{equation}
\end{thm}
%
%We need to emphasise the following 
\begin{rem}\label{rem:vertex:representation}
The conditions of Theorem~\ref{thm:MRPI:set:is:polytopic} require that $\mathcal W(x,u)$ is polytopic
for all finite $(x,u)$, i.e.\ it must have a convex hull representation $\mathcal W(x,u) = \conv_k\{w_k(x,u)\}, k\in\{1,\dots,r\}$ where each 
vertex, $w_k(x,u)$, is a piecewise affine function of $(x,u)$, i.e.
\begin{multline}
	w_k(x,u) = \max\{W_{k,1}^x x + W_{k,1}^u u + w_{k,1}, \\
        W_{k,2}^x x + W_{k,2}^u u + w_{k,2},\dots\}
\end{multline}
where the maximisation is performed elementwise.
\end{rem}}
%
We now derive the representation of $\mathcal Z_m$ and $\mathcal X_m$ as defined in~\eqref{eq:definition:stage:constraints}.
According to Theorem~\ref{thm:MRPI:set:is:polytopic} the MRPI set $\mathcal X^\infty$ is polytopic and has the 
representation~\eqref{eq:halfspace:representation:MRPI}. Therefore the recursion~\eqref{eq:definition:mixed:stage:constraint}
defines $\mathcal Z_1$ as
\begin{equation}\label{eq:derivation:of:mpLP:stage:constraints}
\begin{aligned}
	\mathcal Z_1 =& (\mathbb R^n\times\mathcal U)\cap 
\begin{aligned}[t] \Bigl\{(x,u): \Lambda_{0,i}(Ax&+Bu+Dw)\leq \lambda_{0,i} \\
& \forall w\in\mathcal W(x,u),\, i\in\mathcal I_0 \Bigr\} \end{aligned}
\\
	=&\begin{aligned}[t] (\mathbb R^n & \times \mathcal U) \cap\Bigl\{ (x,u): \\
& \max_{w\in\mathcal W(x,u)}\Lambda_{0,i}(Ax+Bu+Dw)\leq\lambda_{0,i},\, \forall i\in\mathcal I_0 \Bigr\} \end{aligned}
\\
	=&\begin{aligned}[t] & (\mathbb R^n \times\mathcal U)\cap \Bigl\{ (x,u): \\
& \!\!\!\!\!\!
\Lambda_{0,i}(Ax+Bu)+ \!\!\underbrace{\max_{j\in\{1,\dots,r\}}\!\Lambda_{0,i} Dw_j(x,u)}_{(i)}\leq\lambda_i, \, \forall i\in\mathcal I_0
	\Bigr\} \end{aligned}
\end{aligned}
\end{equation}
Since the maximisation $(i)$ in \eqref{eq:derivation:of:mpLP:stage:constraints} is a multi-parametric
linear program, its solution is piecewise affine in $(x,u)$. 
Therefore the set $\mathcal Z_1$ has a representation
$\mathcal Z_1=\{(x,u):\Xi^x_{1,i}x+\Xi^u_{1,i}u\leq\xi_{1,i},i\in\mathcal J_1\}$, with~$\mathcal J_1$ denoting
its index set. The projection~$\mathcal X_1$ 
of $\mathcal Z_1$ onto~$\mathbb R^n$ therefore has the representation~$\mathcal X_1 = \{x:\Lambda_{1,i} x\leq\lambda_{1,i},i\in\mathcal I_1\}$.
From here the determination of $\mathcal Z_k$ and $\mathcal X_k$ follows recursively. We are now able to formulate 
all constraints in~\eqref{eq:the:problem} as inequalities. In the next section we discuss a method of solving
min-max programs such as~\eqref{eq:the:problem} efficiently.

@@

any purpose. \edit{For a general mpQP, the condition~\eqref{mpQP:compatability:assumption} ensures that~\eqref{mpQP:primal}

@@

problem; hence~\eqref{mpQP:compatability:assumption} can be enforced by imposing it as a constraint (which we call a compatibility constraint) on $\theta$ in that problem.}

@@

We recursively define all primal and dual variables:
\begin{equation}\label{eq:trajectory:affine:representation}
	\begin{split}
		u_N(x_N) =& \underbrace{K_{x,N}^u}_{\Psi_N^u} x_N + \underbrace{k_N^u}_{\psi_N^u}\\
		\nu_N(x_N,\beta_N) &= \underbrace{L_{x,N}^\nu}_{\Psi_N^\nu} x_N + \underbrace{L_{\beta,N}^\nu}_{\Phi_N^\nu} \beta_N + 
		\underbrace{l_N^\nu}_{\psi_N^u}\\
		&\vdots \\
		x_0(x_N) =& \underbrace{M_{z,1}^{x^+}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right)}_{\Psi_1^x}x_N + 
		\underbrace{M_{z,1}^{x^+}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + m_1^{x^+}}_{\psi^x_1}\\
		\eta_1(x_N,\beta_N) =& \underbrace{\left(N_{z,1}^{\eta}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right) + 
		N_{\hat\beta,1}^\eta \Psi_1^{\hat\zeta}\right)}_{\Psi_1^\eta}x_N + \underbrace{N_{\hat\beta,1}^\eta \Phi_1^{\hat\zeta}}_{\Phi_1^\eta} \beta_N\\
		&+\underbrace{N_{z,1}^{\eta}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + 
		N_{\hat\beta,1}^\eta \psi_1^{\hat\zeta} + n_1^\eta}_{\psi_1^\eta}
%\\
%		&\vdots
	\end{split}
\end{equation}
Notice that $\Phi^{(\cdot)}_m$ is only non-trivial if the associated sub-problem is degenerate. The
representation~\eqref{eq:trajectory:affine:representation} is valid as long as the constraint set remains
unchanged, i.e.\ the inequalities that hold with equality do not change.
\textcolor{red}{With~\eqref{eq:trajectory:affine:representation} we can justify \edit{choosing the degeneracy parameters as
$\beta_m=\zeta_{m+1}$ and $\hat\beta_m=\hat\zeta_m$. When a constraint is activated the associated dual variable starts at zero and depends affinely on $(x_N,\beta_N)$.
%changesin an affine way in the appropriate direction, 
When the active constraints of a sub-problem become linearly dependent three things happen: the dual variables to the degenerate constraints
depend on an additional degeneracy parameter, a compatibility constraint is introduced in the predecessor
problem, and that compatibility constraint's dual variable is given as a affine function starting at zero,
while all other sub-problems are not affected by the degeneracy. Through} the proposed choice we couple
the degeneracy variable to dual variable of the associated compatibility constraint, hence adding an 
additional affine function to the already affine representation of the dual variable and thereby ensuring continuity
of the dual variable.}

>>>>

In almost all existing methods for RMPC, the model disturbances are assumed to be confined to sets that are constant, 
i.e.~independent of the system state and control inputs. Disturbances that depend on model states (or control inputs) 
are considered in~\cite{Kuntsevich:1995,Rakovic:2006}. However general formulations of state and input dependence can 
result in non-convex constraints~\citep{Rakovic:2006}. To avoid this we make use of recent algorithmic 
advances~\citep{Schaich:2015} that enable a class of polytopic disturbance sets that depend affinely on the system 
state and control input to be handled using convex constraints. This provides an algorithmic and analytical framework 
which is used in the
current paper to embed affine state and input dependent disturbance constraints into the framework of the
active set RMPC solver framework proposed by~\cite{Buerger:2011}. Disturbances that belong to sets which depend
on model states and inputs can account for multiplicative model uncertainty as well as linearisation
errors, and the approach of this paper is therefore able to handle linearisation errors in RMPC non-conservatively.

@@

\section{Problem Statement}\label{sec:problem:statement}
We consider a computationally efficient method for solving online min-max receding horizon control problems
that exploits the structure of multi-parametric programming solutions. Our approach determines the optimal
feedback law without approximating the cost or the constraints of the problem, and without making restrictive
assumptions on the parametrisation of control inputs.
%This broadens the applicability of the approach, allowing for higher order models and longer
%prediction horizons than 
%
%The high computational complexity of online min-max receding horizon control schemes generally requires either
%that the solution is approximated or that their application is limited to problems involving simple system models and short horizons. Here we consider an
%efficient method for solving min-max problems that exploits the structure of multi-parametric programming
%solutions.
%The set of systems to which a min-max robust receding horizon control scheme can be applied online 
%without approximating the solution is bounded by the system complexity. The way to solve min-max problems we 
%adopt here, is to use the structure of the solution to derive multi-parametric programs that can be solved
%efficiently. In order to be able to obtain a closed form solution of the min-max program simple optimisation
%formulations have to be
%The algorithmic treatment of min-max problems
%involving state constraints and disturbances constrained to lie in fixed polytopic disturbance sets was
%introduced in~\cite{Bertsekas:1971}. Recently~\cite{Schaich:2015} proposed an algorithm to compute the so called maximal
%robust positive invariant (MRPI) sets (see~\cite{blanchini:2007}) for linear systems subject to state and
%input dependent disturbance constraints. In this paper we develop the algorithm further
%to compute polytopic constraints necessary to satisfy state constraints robustly in this setup. We
%present a robust receding horizon control scheme for
%
To make it possible to obtain a closed form solution of the min-max optimal control problem we assume a
linear-quadratic problem formulation. Thus we assume linear dynamics 
\begin{equation}\label{eq:system:equation}
	x^+ = A x + B u + D w,
\end{equation}
%
where $A,B,D$ are real matrices of appropriate dimension, $x,  x^+\in\mathcal X\subseteq\mathbb R^n$ denote the state 
and successor state respectively, $u\in\mathcal U=\{u:F_iu\leq 1\,\forall i\in\mathcal I^{\mathcal U}\}
\subset\mathbb R^p$ is the control input
and $w\in\mathcal W(x,u)\subset\mathbb R^q$ is an unknown disturbance input, $\mathcal I^{\mathcal U}$ denotes
the index set of the constraint set~$\mathcal U$. The disturbance set $\mathcal
W(x,u)$ is assumed to have a known dependence on the values of $x$ and $u$, according to
%
\begin{equation}\label{eq:PWA:def:disturbance}
	\mathcal W(x,u) = \{w: Gw \leq H(x,u)\},
\end{equation}
%
where each element of $H(x,u)$ is a convex, piecewise affine function for all $(x,u)\in\mathcal X\times\mathcal U$. 
%\edit{where $H(x,u)$ is an elementwise convex, piecewise affine function}.
The control objective is to minimize the
worst case value, over all future model uncertainty, of the cost
\begin{equation}\label{eq:quadratic:cost}
\sum_{k=0}^\infty \bigl( \norm{x_k}_Q^2 + \norm{u_k}_R^2 - \gamma^2 \norm{w_k}^2 \bigr) ,
\end{equation}
where the subscript $k$ denotes the realisation of a variable at time $k$, $\norm{x}_Q^2$ denotes the quadratic
form $x^TQx$, $Q$ and $R$ are given positive definite
matrices and $\gamma$ is a given scalar weight that controls the $l^2$-gain of the closed loop system from the
disturbance sequence to the state and control sequences.

@@

\section{Controllable sets}\label{sec:preliminaries}
In this section we summarise results on controllable sets that allow the constraints of the problem~\eqref{eq:the:problem} 
to be formulated in a convenient way. The following result shows that the MRPI set (\ref{eq:definition:MRPI:set}) 
associated with the pointwise polytopic set~\eqref{eq:PWA:def:disturbance} is polytopic if $H$ is elementwise convex 
and piecewise affine. For a proof and detailed discussion of this result we refer the reader to~\cite{Schaich:2015}.
%
\begin{thm}[\cite{Schaich:2015}]\label{thm:MRPI:set:is:polytopic}
Let $\mathcal X \subseteq \{x:\Gamma x\leq{\bf{1}}\wedge-\Gamma x\leq{\bf{1}}\}$ be a polyhedral set, let the pair $(A+BK,\Gamma)$ be
observable, and let $\mathcal W(x,Kx)$ be defined as in~\eqref{eq:PWA:def:disturbance} with an elementwise convex piecewise
affine function $H(x,Kx)$ which is bounded for all finite $x$. Then the MRPI set $\mathcal X^\infty$ is polytopic, i.e.\ it has the representation 
\begin{equation}\label{eq:halfspace:representation:MRPI}
	\mathcal X^\infty=\{x:\Lambda_i x\leq \lambda_i, \forall\, i\in\mathcal I^\infty\}.
\end{equation}
\end{thm}
%
%We need to emphasise the following 
\begin{rem}\label{rem:vertex:representation}
The conditions of Theorem~\ref{thm:MRPI:set:is:polytopic} require that $\mathcal W(x,u)$ is polytopic
for all finite $(x,u)$, i.e.\ it must have a convex hull representation $\mathcal W(x,u) = \conv_k\{w_k(x,u)\}, k\in\{1,\dots,r\}$ where each 
vertex, $w_k(x,u)$, is a piecewise affine function of $(x,u)$, i.e.
\begin{multline}
	w_k(x,u) = \max\{W_{k,1}^x x + W_{k,1}^u u + w_{k,1}, \\
        W_{k,2}^x x + W_{k,2}^u u + w_{k,2},\dots\}
\end{multline}
where the maximisation is performed elementwise.
\end{rem}
%
We now derive the representation of $\mathcal Z_m$ and $\mathcal X_m$ as defined in~\eqref{eq:definition:stage:constraints}.
According to Theorem~\ref{thm:MRPI:set:is:polytopic} the MRPI set $\mathcal X^\infty$ is polytopic and has the 
representation~\eqref{eq:halfspace:representation:MRPI}. Therefore the recursion~\eqref{eq:definition:mixed:stage:constraint}
defines $\mathcal Z_1$ as
\begin{equation}\label{eq:derivation:of:mpLP:stage:constraints}
\begin{aligned}
	\mathcal Z_1 =& (\mathbb R^n\times\mathcal U)\cap 
\begin{aligned}[t] \Bigl\{(x,u): \Lambda_{0,i}(Ax&+Bu+Dw)\leq \lambda_{0,i} \\
& \forall w\in\mathcal W(x,u),\, i\in\mathcal I_0 \Bigr\} \end{aligned}
\\
	=&\begin{aligned}[t] (\mathbb R^n & \times \mathcal U) \cap\Bigl\{ (x,u): \\
& \max_{w\in\mathcal W(x,u)}\Lambda_{0,i}(Ax+Bu+Dw)\leq\lambda_{0,i},\, \forall i\in\mathcal I_0 \Bigr\} \end{aligned}
\\
	=&\begin{aligned}[t] & (\mathbb R^n \times\mathcal U)\cap \Bigl\{ (x,u): \\
& \!\!\!\!\!\!
\Lambda_{0,i}(Ax+Bu)+ \!\!\underbrace{\max_{j\in\{1,\dots,r\}}\!\Lambda_{0,i} Dw_j(x,u)}_{(i)}\leq\lambda_i, \, \forall i\in\mathcal I_0
	\Bigr\} \end{aligned}
\end{aligned}
\end{equation}
Since the maximisation $(i)$ in \eqref{eq:derivation:of:mpLP:stage:constraints} is a multi-parametric
linear program, its solution is piecewise affine in $(x,u)$. 
Therefore the set $\mathcal Z_1$ has a representation
$\mathcal Z_1=\{(x,u):\Xi^x_{1,i}x+\Xi^u_{1,i}u\leq\xi_{1,i},i\in\mathcal J_1\}$, with~$\mathcal J_1$ denoting
its index set. The projection~$\mathcal X_1$ 
of $\mathcal Z_1$ onto~$\mathbb R^n$ therefore has the representation~$\mathcal X_1 = \{x:\Lambda_{1,i} x\leq\lambda_{1,i},i\in\mathcal I_1\}$.
From here the determination of $\mathcal Z_k$ and $\mathcal X_k$ follows recursively. We are now able to formulate 
all constraints in~\eqref{eq:the:problem} as inequalities. In the next section we discuss a method of solving
min-max programs such as~\eqref{eq:the:problem} efficiently.

@@

any purpose. For a general mpQP, the condition~\eqref{mpQP:compatability:assumption} ensures that~\eqref{mpQP:primal}

@@

problem; hence~\eqref{mpQP:compatability:assumption} can be enforced by imposing it as a constraint (which we call a compatibility constraint) on $\theta$ in that problem.

@@

We recursively define all primal and dual variables:
\begin{equation}\label{eq:trajectory:affine:representation}
	\begin{split}
		u_N(x_N) =& \underbrace{K_{x,N}^u}_{\Psi_N^u} x_N + \underbrace{k_N^u}_{\psi_N^u}\\
		\nu_N(x_N,\beta_N) &= \underbrace{L_{x,N}^\nu}_{\Psi_N^\nu} x_N + \underbrace{L_{\beta,N}^\nu}_{\Phi_N^\nu} \beta_N + 
		\underbrace{l_N^\nu}_{\psi_N^u}\\
		&\vdots \\
		x_0(x_N) =& \underbrace{M_{z,1}^{x^+}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right)}_{\Psi_1^x}x_N + 
		\underbrace{M_{z,1}^{x^+}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + m_1^{x^+}}_{\psi^x_1}\\
		\eta_1(x_N,\beta_N) =& \underbrace{\left(N_{z,1}^{\eta}\left(\begin{array}{c} \Psi_2^x \\ \Psi_1^u \end{array}\right) + 
		N_{\hat\beta,1}^\eta \Psi_1^{\hat\zeta}\right)}_{\Psi_1^\eta}x_N + \underbrace{N_{\hat\beta,1}^\eta \Phi_1^{\hat\zeta}}_{\Phi_1^\eta} \beta_N\\
		&+\underbrace{N_{z,1}^{\eta}\left(\begin{array}{c} \psi_2^x \\ \psi_1^u \end{array}\right) + 
		N_{\hat\beta,1}^\eta \psi_1^{\hat\zeta} + n_1^\eta}_{\psi_1^\eta}
%\\
%		&\vdots
	\end{split}
\end{equation}
Notice that $\Phi^{(\cdot)}_m$ is only non-trivial if the associated sub-problem is degenerate. The
representation~\eqref{eq:trajectory:affine:representation} is valid as long as the constraint set remains
unchanged, i.e.\ the inequalities that hold with equality do not change.
With~\eqref{eq:trajectory:affine:representation} we can justify choosing the degeneracy parameters as
$\beta_m=\zeta_{m+1}$ and $\hat\beta_m=\hat\zeta_m$. When a constraint is activated the associated dual variable starts at zero and depends affinely on $(x_N,\beta_N)$.
%changesin an affine way in the appropriate direction, 
When the active constraints of a sub-problem become linearly dependent three things happen: the dual variables to the degenerate constraints
depend on an additional degeneracy parameter, a compatibility constraint is introduced in the predecessor
problem, and that compatibility constraint's dual variable is given as a affine function starting at zero,
while all other sub-problems are not affected by the degeneracy. Through the proposed choice we couple
the degeneracy variable to dual variable of the associated compatibility constraint, hence adding an 
additional affine function to the already affine representation of the dual variable and thereby ensuring continuity
of the dual variable.
